Modern BTree\\ techniques

### 2020-01-07 btree/presentation.tex
Add normalization & prefix truncation

>>>>

    \begin{center}
    \textbf{Key normalization}
    \vspace{1cm}

    \begin{tabular}{cccl}
        1 & "Dirk" & "Bart" &
            \colorbox{BurntOrange}{1}
            \colorbox{SpringGreen}{0..01}
            \colorbox{BurntOrange}{1}
            \colorbox{SpringGreen}{11..00}
            \colorbox{Gray!40}{$\emptyset$}
            \colorbox{BurntOrange}{1}
            \colorbox{SpringGreen}{10..10}
            \colorbox{Gray!40}{$\emptyset$} \\
        2 & "Todd" & Null &
            \colorbox{BurntOrange}{1}
            \colorbox{SpringGreen}{0..10}
            \colorbox{BurntOrange}{1}
            \colorbox{SpringGreen}{01..00}
            \colorbox{Gray!40}{$\emptyset$}
            \colorbox{BurntOrange}{0} \\
        Null & "" & Null &
            \colorbox{BurntOrange}{0}
            \colorbox{BurntOrange}{1}
            \colorbox{Gray!40}{$\emptyset$}
            \colorbox{BurntOrange}{0} \\
    \end{tabular}

    \end{center}
\end{frame}
\note{
    https://wiki.postgresql.org/wiki/Key_normalization

    Should be not used for leaves, since normalization looses the information.
    Other option is too store both normalized and original key values.
}

    \begin{center}
    \textbf{Prefix truncation}
    \vspace{1cm}

    \begin{overprint}[8cm]
        \onslide<1>
        \begin{tabular}{lll}
            & & \\
            & Smith Jack & 01-02-2019 \\
            & Smith Jane & 02-03-2019 \\
            & Smith James & 03-04-2019 \\
        \end{tabular}

        \onslide<2>
        \begin{tabular}{lll}
            & & \\
            & \colorbox{BurntOrange}{Smith Ja}ck & 01-02-2019 \\
            & \colorbox{BurntOrange}{Smith Ja}ne & 02-03-2019 \\
            & \colorbox{BurntOrange}{Smith Ja}mes & 03-04-2019 \\
        \end{tabular}

        \onslide<3>
        \begin{tabular}{lll}
            \colorbox{BurntOrange}{Smith Ja} & & \\
            & ck & 01-02-2019 \\
            & ne & 02-03-2019 \\
            & mes & 03-04-2019 \\
        \end{tabular}

        \onslide<4>
        \begin{tikzpicture}[]
            \btreenodewithitems{1}{5}{4}{}{btree-leaf}
        \end{tikzpicture}

    \end{overprint}

    \end{center}
\end{frame}
\note{
    BerkleyDB, https://web.stanford.edu/class/cs276a/projects/docs/berkeleydb/api_c/db_set_bt_prefix.html
}

    \begin{center}
    \textbf{Dynamic prefix truncation}
    \vspace{1cm}

    \begin{overprint}[8cm]
    \end{overprint}
